Fail Faster

### 2025-03-24 paper/paper.tex
scala
more consistent figure text size
gnenerators

% \subsubsection{Function call overhead}
\subsection{Inefficient Randomness Libraries}
\label{subsection:ineff-rand}
The core of any PBT generator library is a source of randomness.
Different PBT libraries use different randomness libraries implementing different algorithms
\footnote{The common term for such an algorithm or library is a ``Random Number
Generator'' (RNG). We will avoid this term and instead say ``randomness library''
to avoid confusing RNG implementations with the PBT gnenerator libraries that
use them.}.
Following the original Haskell QuickCheck implementation, \bq\ uses the SplitMix
algorithm~\cite{splitmix}, implemented by \texttt{Splittable\_random}. Meanwhile,
ScalaCheck uses the JSF algorithm~\cite{jsf}.
% https://www.pcg-random.org/posts/bob-jenkins-small-prng-passes-practrand.html
% https://burtleburtle.net/bob/rand/smallprng.html

@@

>>>>

% \subsubsection{Function call overhead}
\subsection{Inefficient Randomness Libraries}
\label{subsection:ineff-rand}
The core of any PBT generator library is a source of randomness.
Different PBT libraries use different randomness libraries implementing different algorithms
\footnote{The common term for such an algorithm or library is a ``Random Number
Generator'' (RNG). We will avoid this term and instead say ``randomness library''
to avoid confusing RNG implementations with the PBT generator libraries that
use them.}.
Following the original Haskell QuickCheck implementation, \bq\ uses the SplitMix
algorithm~\cite{splitmix}, implemented by \texttt{Splittable\_random}. Meanwhile,
ScalaCheck uses the JSF algorithm~\cite{jsf}.
% https://www.pcg-random.org/posts/bob-jenkins-small-prng-passes-practrand.html
% https://burtleburtle.net/bob/rand/smallprng.html

@@

\subsection*{Data Availabilty Statement}
For artifact evaluation we will submit (1) the source code of \camlname{} and \scalaname{} as well as (2) the code for our version of Etna,
which we have modified slightly to pass deterministic seeds to all versions of a single strategy.
These programs are not available publicly or anonymized at the time of submission.
